CODE CHECK

### 2020-02-06 codecheck-paper.Rmd
Update codecheck-paper.Rmd

- **Principles**: https://codecheck.org.uk/
- relation to "proper" citation of data and software, and depositing of data and software in suitable repos _besides_ the bundle for CODE CHECK: do it, only provide the concrete analysis script for the check
- **Why is it useful?**
  - reduce the barrier to evaluating non-text parts of research
  - acknowledges different skill sets and existing high load on reviewers
  - CC breaks problem that publishers staff expertise today is not likely to suffice
  - engaging ECRs is a perfet fit (they are up-to-date in methods, are introduced to peer review)
  - relation to research compendia? point it out for authors unsure about how to structure their workflow
  - CrossRef and Publons and ORCID have features around reviews
  - shifting burden from reviewer to author (but not too much)
- keynote https://doi.org/10.7557/5.4963: in discussion, the speaker mentioned value of peer review for "baseline reassurance", i.e. a paper has at least been checked by someone with an understanding, to increase trust especially if looking at papers from other disciplines
- **report** must fulfil some requirements to make clear what is really checked and not mislead - readers will have very different understandings of a green checkmark!

@@

- https://paperpile.com/shared/rVNwBS
- https://medium.com/bits-and-behavior/a-modern-vision-for-peer-review-d5f73f0fae07 - work by Amy J. Ko: https://faculty.washington.edu/ajko/publications
  - is CODE CHECK's process too small, too incremental a change?
- _Successes and struggles with computational reproducibility: Lessons from the Fragile Families Challenge_ > https://osf.io/preprints/socarxiv/g3pdb/
- community standards for software, cf. slide 6 in https://figshare.com/articles/_/5675104
  - "good enough practice" is "get a colleague to try using it", slide 19 in https://figshare.com/articles/_/5675104
- journals doing code reviews
  - _"We know of 16 journals that take this valuable step (ie TOP Level 3): AEA as already mentioned, plus others in polisci, psychology, biostats, and org chem: see Data Rep Policies here https://t.co/plOF8j6ADU "_ (https://twitter.com/EvoMellor/status/1202692360456589339?s=09); see also whole thread!
  - https://medium.com/@NeurIPSConf/call-for-papers-689294418f43
  - https://www.journals.elsevier.com/information-systems/editorial-board/
  - SIGMOD Reproducibility Review?
  - Biostatistics "AER" (https://academic.oup.com/biostatistics/article/10/3/405/293660)
- open science platforms/cloud services > https://www.nature.com/articles/d41586-019-03366-x
- live code in articles > o2r, eLife RDS https://www.nature.com/articles/d41586-019-00724-7, ...
- Artefact Evaluation - https://www.artifact-eval.org/about.html
- continuous analysis - https://www.nature.com/articles/nbt.3780
- "A Universal Identifier for Computational Results" > https://www.sciencedirect.com/science/article/pii/S1877050911001256
- Discussion about using Docker containers during JOSS reviews > https://github.com/openjournals/joss/issues/498#issuecomment-462046912

@@

- **the default implementation**
- critically discuss our/the default implementation vs. the principles
- HPC example

>>>>

- **Principles**: https://codecheck.org.uk/
- relation to "proper" citation of data and software, and depositing of data and software in suitable repos _besides_ the bundle for CODE CHECK: do it, only provide the concrete analysis script for the check
- **Why is it useful?**
  - reduce the barrier to evaluating non-text parts of research
  - acknowledges different skill sets and existing high load on reviewers
  - CC breaks problem that publishers staff expertise today is not likely to suffice
  - engaging ECRs is a perfet fit (they are up-to-date in methods, are introduced to peer review)
  - relation to research compendia? point it out for authors unsure about how to structure their workflow
  - CrossRef and Publons and ORCID have features around reviews
  - shifting burden from reviewer to author (but not too much)
- keynote https://doi.org/10.7557/5.4963: in discussion, the speaker mentioned value of peer review for "baseline reassurance", i.e. a paper has at least been checked by someone with an understanding, to increase trust especially if looking at papers from other disciplines
- **report** must fulfil some requirements to make clear what is really checked and not mislead - readers will have very different understandings of a green checkmark!
- reproducibility is hard https://twitter.com/annakrystalli/status/1144176149859377152?ref_src=twsrc%5Etfw > code check gives at least some benefits

@@

- https://paperpile.com/shared/rVNwBS
- https://medium.com/bits-and-behavior/a-modern-vision-for-peer-review-d5f73f0fae07 - work by Amy J. Ko: https://faculty.washington.edu/ajko/publications
  - is CODE CHECK's process too small, too incremental a change?
- _Successes and struggles with computational reproducibility: Lessons from the Fragile Families Challenge_ > https://osf.io/preprints/socarxiv/g3pdb/
- community standards for software, cf. slide 6 in https://figshare.com/articles/_/5675104
  - "good enough practice" is "get a colleague to try using it", slide 19 in https://figshare.com/articles/_/5675104
- journals doing code reviews
  - _"We know of 16 journals that take this valuable step (ie TOP Level 3): AEA as already mentioned, plus others in polisci, psychology, biostats, and org chem: see Data Rep Policies here https://t.co/plOF8j6ADU "_ (https://twitter.com/EvoMellor/status/1202692360456589339?s=09); see also whole thread!
  - https://medium.com/@NeurIPSConf/call-for-papers-689294418f43
  - https://www.journals.elsevier.com/information-systems/editorial-board/
  - SIGMOD Reproducibility Review?
  - Biostatistics "AER" (https://academic.oup.com/biostatistics/article/10/3/405/293660)
- open science platforms/cloud services > https://www.nature.com/articles/d41586-019-03366-x
- live code in articles > o2r, eLife RDS https://www.nature.com/articles/d41586-019-00724-7, ...
- Artefact Evaluation - https://www.artifact-eval.org/about.html
- continuous analysis - https://www.nature.com/articles/nbt.3780
- "A Universal Identifier for Computational Results" > https://www.sciencedirect.com/science/article/pii/S1877050911001256
- Discussion about using Docker containers during JOSS reviews > https://github.com/openjournals/joss/issues/498#issuecomment-462046912
- https://scigen.report, an independent site for registering reproductions, via https://annakrystalli.me/talks/ro-reprohack.html#32
  - example https://scigen.report/reviews/get?doi=10.1063/1.1823034
  - seems to be closed infrastructure

@@

- **the default implementation**
- critically discuss our/the default implementation vs. the principles
- HPC example
- if we see the corpus of examles as a scientific dataset, it should be published in a citable way (maybe even submit to a data journal)
